A Survey of Fuzzing and New Technique for Dynamic Analysis

### 2014-03-10 docs/paper/fsuthesis/thesis-template/paper.tex
added some stuff TODO and planned last few pages

\section{Motivation}
TODO US gov't interest via money, security issues, etc.

@@

TODO should this section be moved from prelims elsewhere?

@@

TODO one-way functs

@@

Used in javascript fuzzer [AD]
Used in [C].

@@

As a demonstration I have run my fuzzer, Stubble, against various binaries which open a file and check specific bytes in a file for specific character values. If all of these checks pass, then AAAAA, otherwise BBBBBB (segfault? EIP? add vulnerability detection alg?). I have observed .... (insert graphs with password lengths, etc.)

@@

I have implemented a parallel version of the pintool, mp.c, to fork and exec a user-specified number of processes. Because a tainted branch may only be reachable based upon previous branches taken, and also because of complex conditions involving loops, the problem is not embarassingly parallel. For this project I have tested my program on a personally created binary, simpleCrackme. This binary takes a file containing a password in argv1. If the password matches its secret, then it prints "You win", otherwise, it prints "You lose".

After running my program, one can grep for the win string in the output/ directory. This is similar to concept to running a fuzzer, and grepping around the output recorded for more interesting conditions, like segfaults. Results show a noticeable speedup.

@@

%Looking like linear with password + constant of 16 overtaint
%Pw len:   Tests: 
%1         17
%4         20
%7         26
%10        28

%\begin{filecontents*}{results.txt}
%	$x$	$y$       
%	1	17
%	4	20
%    7	26
%    10	28
%\end{filecontents*}

%\pgfplotsset{results.txt}

\begin{tikzpicture}
\begin{axis}[
    title={Oracle Attack},
    xlabel={Secret Length},
    ylabel={Test cases},
    xmin=0, xmax=15,
    ymin=10, ymax=30,
    xtick={0,2,4,6,8,10},
    ytick={15,20,25,30},
    ymajorgrids=true,
    grid style=dashed,
]

\addplot[
    color=blue,
    mark=square,
    ]
    coordinates {
    		(1,17)
    		(4,20)
    		(7,26)
    		(10,28)
    		(15,38)
    }; 
\end{axis}
\end{tikzpicture}

@@

TODO overtainting, naive implementations had LOTS of it

@@

	\item [Z] Peach Fuzzer. \url{<http://peachfuzzer.com/>}

@@

>>>>

\section{Motivation}
TODO US gov't interest via money, security issues, etc.
Raytheon SI/VUPEN use it.

@@

TODO add code examples
%http://en.wikipedia.org/wiki/User_Datagram_Protocol#IPv4_Pseudo_Header
IDEA write c program to checksum UDP packets and say whether they pass or not, have fuzzer "correct" packets to pass arbitrary, user decided checksum.
update: probably will not work without noticeable modification, but could maybe notice the situation and reverse engineer the algorithm, then print it out or start making a lookup table?

@@

TODO one-way functs
Use: https://www.ida.liu.se/~TDDC90/literature/papers/violating05.pdf
[AJ]

@@

Used in javascript fuzzer [AD]
Used in [C].
Mitigates dealing with side effects, done by PANDA.
%http://www.cc.gatech.edu/~brendan/tzb_author.pdf
%http://iris.lib.neu.edu/cgi/viewcontent.cgi?article=1097&context=elec_comp_theses

@@

As a demonstration I have run my fuzzer, Stubble, against various binaries which open a file and check specific bytes in a file for specific character values. If all of these checks pass, then the program outputs a "win" string, otherwise it outputs a "lose" string. This can be thought of conceptually as an oracle attack, and is similar to reverse engineering "crackme" exercises. Given no knowledge of the secret key, and only able to query an oracle, a successful attack must discover the secret within a reasonable number of guess [CITE?].

After compiling with the Tiny C Compiler, which performs minimal optimization and doesn't add security measures, this binary and a default test file are given as input to Stubble, which will begin to dynamically generate run cases which will explore new paths within the binary. These test cases are fed back into the system, which continues to backsolve to find new ways to explore at branches, until there are no tainted bytes left for exploration.

% (segfault? EIP? add vulnerability detection alg?). I have observed .... (insert graphs with password lengths, etc.)

Secrets of length 1 to 50 were tested at various intervals. It appears that, aside from some constant overhead, that test cases generated and time required to crack the binary  rise linearly with password length. The constant overhead is probably introduced from overtaint.

(TODO time smaller oracle attacks)
TODO attacks which transform input first to show ability to backsolve

\begin{tikzpicture}
\begin{axis}[
    title={Oracle Attack},
    xlabel={Secret Length},
    ylabel={Test cases},
    xmin=0, xmax=55,
    ymin=10, ymax=100,
    xtick={0,10,20,30,40,50},
    ytick={20,30,40,50,60,70,80,90,100},
    ymajorgrids=true,
    grid style=dashed,
]

\addplot[
    color=blue,
    mark=square,
    ]
    coordinates {
    		(1,17)
    		(4,20)
    		(7,26)
    		(10,28)
    		(15,38)
    		(20, 45)
    		(25, 53) % 1:41.22elapsed
    		(30, 60) % 1:51.78elapsed
    		(35, 67) % 2:09.49elapsed
    		(40, 74) % 2:19.83elapsed
    		(45, 82) % 2:36.96elapsed
    		(50, 90) % 2:51.77elapsed
    }; 
\end{axis}
\end{tikzpicture}

\begin{tikzpicture}
\begin{axis}[
    title={Oracle Attack},
    xlabel={Secret Length},
    ylabel={Time Elapsed (seconds)},
    xmin=0, xmax=55,
    ymin=10, ymax=200,
    xtick={0,10,20,30,40,50},
    ytick={0,20,30,40,50,60,80,100,120,140,160,180,200},
    ymajorgrids=true,
    grid style=dashed,
]

\addplot[
    color=red,
    mark=square,
    ]
    coordinates {
    		(1,0) % TODO time these first couple
    		(4,0)
    		(7,0)
    		(10,0)
    		(15,0)
    		(20, 0)
    		(25, 101) 
    		(30, 112)
    		(35, 129) 
    		(40, 140)
    		(45, 157) 
    		(50, 172) 
    }; 
\end{axis}
\end{tikzpicture}

@@

I have implemented a parallel version of the pintool, mp.c, to fork and exec a user-specified number of processes. Because a tainted branch may only be reachable based upon previous branches taken, and also because of complex conditions involving loops, the problem is not embarassingly parallel. Results show an expected speedup for an application with decently independent input.

@@

@@

TODO overtainting, naive implementations had lots of it.
TODO difficulties with implementation

@@

	\item [Z] Eddington, Michael. "Peach fuzzing platform." Peach Fuzzer (2011).

@@

	\item [AJ] Oehlert, Peter. "Violating assumptions with fuzzing." Security \& Privacy, IEEE 3.2 (2005): 58-62.
